Attribute fusion in a latent process model for time series of graphs

### 2011-04-28 ssp2011.tex
Add proofs of multinormal approximation

  \caption{Temporal standardization: when testing for change at time $t$, the recent past (graphs $G(t - l), \dots, G(t-1))$ is used to standardize the invariants}

@@

  Let $a_n$ and $b_n$ be constants given by

@@

     \mathcal{G}(a_n \sigma_2 + \mu_2, b_n \sigma_2) &

@@

    \mu_1 &= (n-1)\langle x, \pi_{00} \rangle \\
    \sigma_1 &= \sqrt{(n-1)\langle x, \eta_{00} x \rangle} \\

@@

    m)\langle x, \pi_{01} \rangle
    \\ \sigma_2 &= \sqrt{ (m - 1) \langle x, (\eta_{11} x \rangle + (n -
      m) \left<x, \eta_{01} x\right>}

@@

  $l$, the variable $T_{\lambda}^{l}(t)$ has approximately a Gumbel
  distribution with location $\rho_{\lambda}$ and scale $\varsigma_{l}$ where

@@

  \rho_{\lambda} = \begin{cases}
    \frac{ (a_n + b_n \gamma)(\sigma_2 - \sigma_1) + (\mu_2 -
    \mu_1)}{\tfrac{\pi}{\sqrt{6}}\sqrt{(1 + 1/m)\sigma_1^2 +
      (\sigma_2^2 - \sigma_1^2)}} & \text{if $t = t_1$} \\ 
  0 & \text{if $t < t_1$}

@@

$\gamma \approx 0.57721$ is the Euler-Mascheroni constant, and

@@

@@

\bibliography{ssp2011}
\end{document}

>>>>

  \caption{Temporal standardization: when testing for change at time
    $t$, the recent past (graphs $G(t - l), \dots, G(t-1))$ is used to
    standardize the invariants}

@@

  Let $a_n$ and $b_n$ be functions of $n$ given by

@@

     \mathcal{G}(a_m \sigma_2 + \mu_2, b_m \sigma_2) &

@@

    \mu_1 &= (n-1)\langle \lambda, \pi_{00} \rangle \\
    \sigma_1 &= \sqrt{(n-1)\langle \lambda, \eta_{00} \lambda \rangle} \\

@@

    m)\langle \lambda, \pi_{01} \rangle
    \\ \sigma_2 &= \sqrt{ (m - 1) \langle \lambda, \eta_{11} \lambda \rangle + (n -
      m) \langle \lambda, \eta_{01} \lambda \rangle}

@@

  $l$, the variable $T_{\lambda}^{l}(t)$ has approximately a
  $\mathcal{G}(\rho_{\lambda}, \varsigma_{\lambda})$ distribution with
\begin{align}

@@

  \rho_{\lambda} &= \begin{cases}
    \frac{\sqrt{\pi}}{6} \frac{\mu_2 - \mu_1 + a_m\sigma_2 - (a_n + b_n
      \gamma)\sigma_1}{b_n \sigma_1} & \text{if $t =
        t^{*}$} \\
      - \frac{ \sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$}
  \end{cases}\\
  \varsigma_{\lambda} &= \begin{cases}
    \frac{\sqrt{\pi} b_m \sigma_2}{6 b_n \sigma_1} & \text{if $t =
      t^{*}$} \\
    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$}

@@

\end{align}
$\gamma \approx 0.57721$ is the Euler-Mascheroni constant.

@@

power of the test using $\Delta_{\lambda}$. The power approximation is
once again determined by various factors, but the dominating factor is
likely to be $\tfrac{\rho_\lambda}{\varsigma_\lambda}$. For sufficiently large $n$
and $m$, we also have
  \begin{split}
  \frac{\rho_\lambda}{\varsigma_\lambda} &= (1 + o(1)) \frac{\mu_2 - \mu_1}{b_m
    \sigma_ 2} \\ &= \frac{\langle \lambda, (m-1)\pi_{11} + (n-m)\pi_{01} -
    (n-1) \pi_{00} \rangle}{\sqrt{\langle \lambda, ((m-1) \eta_{11} +
    (n-m)\eta_{01}) \lambda \rangle}}
  \end{split}
We can thus find the maximum and minimum of
$\tfrac{\rho_{\lambda}}{\varsigma_{\lambda}}$ by solving an 
eigenvalue problem as in Theorem~\ref{thm:1}. 

@@

\begin{proof}[Proposition~\ref{prop:3}]
  Let $d_{\lambda}(v;t)$ be the (fused) degree of vertex $v$ at time
  $t$, i.e.,
    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{u \in N(v)}
    \mathbf{1}\{ \phi(uv,t) = k \}
  By applying the multivariate normal approximation to the
  multinomial, 

\bibliography{ssp2011}
\end{document}
